---
title: "T1_graduation_project"
author: "Kenza Abellaoui"
date: "16/06/2023"
output: html_document
---
```{r}

library(readxl)

csv_file <- 'C:/Users/surface/OneDrive/Desktop/Graduation_Project/Grad_Proj_Data.xlsx'

T1_data <- read_excel(csv_file, sheet = 'setapProductT1')
columns_to_keep <- c('year', 'semester', 'timeInterval', 'teamNumber', 'semesterId', 'teamMemberCount', 'femaleTeamMembersPercent', 'teamLeadGender', 'teamDistribution', 'teamMemberResponseCount', 'meetingHoursTotal', 'inPersonMeetingHoursTotal', 'nonCodingDeliverablesHoursTotal', 'codingDeliverablesHoursTotal', 'helpHoursTotal', 'globalLeadAdminHoursTotal', 'leadAdminHoursResponseCount', 'globalLeadAdminHoursResponseCount', 'commitCount', 'uniqueCommitMessageCount', 'uniqueCommitMessagePercent', 'commitMessageLengthTotal', 'issueCount', 'onTimeIssueCount', 'lateIssueCount', 'productLetterGrade')

T1_data <- T1_data[, columns_to_keep]
T1_data <- head(T1_data, n= nrow(T1_data)-10)
T1_data$globalLeadAdminHoursTotal[is.na(T1_data$globalLeadAdminHoursTotal)] <- 0


#Add column of encoded team dist
T1_data$teamDistribution_encoded <- ifelse(T1_data$teamDistribution == "Local", 0, 1)
print(T1_data)

str(T1_data)

```
```{r}
gender_counts <- table(T1_data$teamLeadGender)
gender_counts
```

```{r}

numeric_columns <- c('teamMemberCount', 'femaleTeamMembersPercent','teamMemberResponseCount', 'meetingHoursTotal', 'inPersonMeetingHoursTotal', 'nonCodingDeliverablesHoursTotal', 'codingDeliverablesHoursTotal', 'helpHoursTotal', 'globalLeadAdminHoursTotal', 'leadAdminHoursResponseCount', 'globalLeadAdminHoursResponseCount', 'commitCount', 'uniqueCommitMessageCount', 'uniqueCommitMessagePercent', 'commitMessageLengthTotal', 'issueCount', 'onTimeIssueCount','teamDistribution_encoded')

# Filter out the numeric columns
numeric_data <- T1_data[ , numeric_columns]
```

```{r}
print(numeric_data)
```
```{r}
str(numeric_data)
```
```{r}
# Convert character columns to numeric
numeric_data$femaleTeamMembersPercent <- as.numeric(numeric_data$femaleTeamMembersPercent)
numeric_data$meetingHoursTotal <- as.numeric(numeric_data$meetingHoursTotal)
numeric_data$inPersonMeetingHoursTotal <- as.numeric(numeric_data$inPersonMeetingHoursTotal)
numeric_data$nonCodingDeliverablesHoursTotal <- as.numeric(numeric_data$nonCodingDeliverablesHoursTotal)
numeric_data$codingDeliverablesHoursTotal <- as.numeric(numeric_data$codingDeliverablesHoursTotal)
numeric_data$helpHoursTotal <- as.numeric(numeric_data$helpHoursTotal)
numeric_data$globalLeadAdminHoursTotal <- as.numeric(numeric_data$globalLeadAdminHoursTotal)
numeric_data$uniqueCommitMessagePercent <- as.numeric(numeric_data$uniqueCommitMessagePercent)
```


```{r}
str(numeric_data)
```


#
library(ggplot2)

# Create an empty list to store the plots
plots <- list()

# Iterate over each column in the dataframe
for (col in colnames(numeric_data)) {
  # Create a boxplot for the "global" category
  global_plot <- ggplot(numeric_data[numeric_data$teamDistribution_encoded == 1, ], aes(x = 1, y = .data[[col]])) +
    geom_boxplot() +
    labs(title = paste(col, "Global"), x = NULL, y = NULL) +
    theme_light() +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
  
  # Create a boxplot for the other category
  other_plot <- ggplot(numeric_data[numeric_data$teamDistribution_encoded == 0, ], aes(x = 1, y = .data[[col]])) +
    geom_boxplot() +
    labs(title = paste(col, "Local"), x = NULL, y = NULL) +
    theme_light() +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
  
  # Add the plots to the list
  plots[[paste(col, "Global")]] <- global_plot
  plots[[paste(col, "Local")]] <- other_plot
}

# Display the boxplots
for (plot_title in names(plots)) {
  print(plots[[plot_title]])
}



library(dplyr)
library(ggplot2)
library(tidyr)

# Create a list to store the combined boxplot plots
combined_boxplots <- list()

# Iterate over each column in the dataframe
for (col in colnames(numeric_data)) {
  # Prepare the data for plotting
  plot_data <- numeric_data %>%
    select(teamDistribution_encoded, .data[[col]])
  
  # Create the combined boxplot plot
  plot <- ggplot(plot_data, aes(x = factor(teamDistribution_encoded), y = .data[[col]], fill = factor(teamDistribution_encoded))) +
    geom_boxplot() +
    labs(title = col, x = "Category", y = NULL) +
    theme_minimal() +
    facet_wrap(~ teamDistribution_encoded, labeller = labeller(teamDistribution_encoded = c("0" = "Local", "1" = "Global")))
  
  # Add the plot to the list
  combined_boxplots[[col]] <- plot
}

# View the combined boxplot plots
combined_boxplots


library(dplyr)
library(ggplot2)
library(tidyr)

# Create a list to store the combined boxplot plots
combined_boxplots <- list()

# Iterate over each column in the dataframe
for (col in colnames(numeric_data)) {
  # Prepare the data for plotting
  plot_data <- numeric_data %>%
    select(teamDistribution_encoded, .data[[col]])
  
  # Create the combined boxplot plot
  plot <- ggplot(plot_data, aes(x = factor(teamDistribution_encoded), y = .data[[col]], fill = factor(teamDistribution_encoded))) +
    geom_boxplot(show.legend = FALSE) +
    labs(title = col, x = NULL, y = NULL) +
    theme_minimal() +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank()) +
    facet_wrap(~ teamDistribution_encoded, labeller = labeller(teamDistribution_encoded = c("0" = "Local", "1" = "Global")))
  
  # Add the plot to the list
  combined_boxplots[[col]] <- plot
}

# View the combined boxplot plots
combined_boxplots



library(dplyr)
library(ggplot2)
library(tidyr)


# Create a directory to save the plots
dir.create("boxplot_plots")

# Set the theme to have a white background
my_theme <- theme_minimal() +
  theme(panel.background = element_rect(fill = "white", color = NA),
        plot.background = element_rect(fill = "white", color = NA))

# Iterate over each column in the dataframe
for (col in colnames(numeric_data)) {
  # Prepare the data for plotting
  plot_data <- numeric_data %>%
    select(teamDistribution_encoded, .data[[col]])
  
  # Create the combined boxplot plot
  plot <- ggplot(plot_data, aes(x = factor(teamDistribution_encoded), y = .data[[col]], fill = factor(teamDistribution_encoded))) +
    geom_boxplot(show.legend = FALSE) +
    labs(title = NULL, x = NULL, y = NULL) +
    my_theme +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank()) +
    facet_wrap(~ teamDistribution_encoded, labeller = labeller(teamDistribution_encoded = c("0" = "Local", "1" = "Global")))
  
  # Save the plot as an image file without titles
  filename <- paste0("boxplot_plots/", col, "_boxplot.png")
  ggsave(filename, plot, width = 6, height = 4, dpi = 300)
}





library(dplyr)
library(ggplot2)


# Create a directory to save the density plots
dir.create("density_plots")

# Create a list to store the modified density plots
modified_density_plots <- list()

# Iterate over each column in the dataframe
for (col in colnames(numeric_data)) {
  # Calculate mean and standard deviation for the current column
  mean_val <- mean(numeric_data[[col]])
  sd_val <- sd(numeric_data[[col]])

  # Create a density plot for the current column
  plot <- ggplot(numeric_data, aes(x = .data[[col]])) +
    geom_density(fill = "blue", alpha = 0.5) +
    stat_function(fun = dnorm, args = list(mean = mean_val, sd = sd_val),
                  color = "blue", linetype = "dashed", size = 1) +
    labs(title = NULL, x = NULL, y = "Density") +
    theme_minimal() +
    theme(legend.position = "none",
          plot.background = element_rect(fill = "white", color = NA))

  # Save the modified plot as an image file
  filename <- paste0("density_plots/", col, "_density_plot.png")
  ggsave(filename, plot, width = 6, height = 4, dpi = 300)

  # Add the modified plot to the list
  modified_density_plots[[col]] <- plot
}

# View the modified density plots
modified_density_plots




library(dplyr)

# Create a list to store the density plots
density_plots <- list()

# Iterate over each column in the dataframe
for (col in colnames(numeric_data)) {
  # Calculate mean and standard deviation for the current column
  mean_val <- mean(numeric_data[[col]])
  sd_val <- sd(numeric_data[[col]])

  # Create a density plot for the current column
  plot <- ggplot(numeric_data, aes(x = .data[[col]], fill = col)) +
    geom_density(alpha = 0.5) +
    stat_function(fun = dnorm, args = list(mean = mean_val, sd = sd_val),
                  color = "blue", linetype = "dashed", size = 1) +
    labs(title = col, x = col, y = "Density") +
    theme_minimal()

  # Add the plot to the list
  density_plots[[col]] <- plot
}

# View the density plots
density_plots




library(dplyr)
library(ggplot2)

# Create a list to store the density plots
density_plots <- list()

# Iterate over each column in the dataframe
for (col in colnames(numeric_data)) {
  # Calculate mean and standard deviation for the current column
  mean_val <- mean(numeric_data[[col]])
  sd_val <- sd(numeric_data[[col]])

  # Create a density plot for both categories
  plot <- ggplot(numeric_data, aes(x = .data[[col]], fill = col)) +
    geom_density(alpha = 0.5) +
    stat_function(fun = dnorm, args = list(mean = mean_val, sd = sd_val),
                  color = "blue", linetype = "dashed", size = 1) +
    labs(title = col, x = col, y = "Density") +
    theme_minimal() +
    facet_wrap(~ teamDistribution_encoded, labeller = labeller(teamDistribution_encoded = c("0" = "Local", "1" = "Global")))

  # Add the plot to the list
  density_plots[[col]] <- plot
}

# View the density plots
density_plots


oui
library(dplyr)
library(ggplot2)


# Create a directory to save the density plots
dir.create("density_plots_dist")

# Create a list to store the modified density plots
modified_density_plots <- list()

# Iterate over each column in the dataframe
for (col in colnames(numeric_data)) {
  # Calculate mean and standard deviation for the current column
  mean_val <- mean(numeric_data[[col]])
  sd_val <- sd(numeric_data[[col]])

  # Create a density plot for both categories
  plot <- ggplot(numeric_data, aes(x = .data[[col]])) +
    geom_density(fill = "blue", alpha = 0.5) +
    stat_function(fun = dnorm, args = list(mean = mean_val, sd = sd_val),
                  color = "blue", linetype = "dashed", size = 1) +
    labs(title = NULL, x = NULL, y = "Density") +
    theme_minimal() +
    theme(legend.position = "none",
          plot.background = element_rect(fill = "white", color = NA)) +
    facet_wrap(~ teamDistribution_encoded, labeller = labeller(teamDistribution_encoded = c("0" = "Local", "1" = "Global")))

  # Save the modified plot as an image file based on the team distribution category
  filename <- paste0("density_plots_dist/", col, "_density_plot_", unique(numeric_data$teamDistribution_encoded), ".png")
  ggsave(filename, plot, width = 6, height = 4, dpi = 300)

  # Add the modified plot to the list
  modified_density_plots[[col]] <- plot
}

# View the modified density plots
modified_density_plots



```{r}
summary(numeric_data)
```
```{r}


```


```{r}
# Calculate the lower and upper bounds for outlier detection
Q1 <- apply(numeric_data, 2, quantile, 0.25, na.rm = TRUE)
Q3 <- apply(numeric_data, 2, quantile, 0.75, na.rm = TRUE)
IQR <- Q3 - Q1
lower_bound <- Q1 - 1.5 * IQR
upper_bound <- Q3 + 1.5 * IQR

# Identify rows with outliers in numeric columns (excluding "teamDistribution_encoded")
outlier_rows <- apply(numeric_data[-which(names(numeric_data) == "teamDistribution_encoded")], 1, function(row) {
  any(row < lower_bound | row > upper_bound, na.rm = TRUE) || numeric_data$femaleTeamMembersPercent[row] != 0
})

# Remove rows with outliers from the original data frame
data_no_outliers <- T1_data[!outlier_rows, ]


# Identify rows with "Global" in the "teamDistribution_encoded" column
global_rows <- numeric_data$teamDistribution_encoded == 1

# Identify rows where femaleTeamMembersPercent is not equal to zero
non_zero_female_rows <- numeric_data$femaleTeamMembersPercent != 0

# Combine the outlier, global, and non-zero female rows
rows_to_keep <- global_rows | non_zero_female_rows

# Remove rows with outliers from the original data frame
data_no_outliers <- T1_data[rows_to_keep, ]

# Remove rows with outliers from the numeric data
numeric_data_no_outliers <- numeric_data[rows_to_keep, ]
```


library(dplyr)
library(ggplot2)
library(tidyr)

# Create a list to store the combined boxplot plots
combined_boxplots <- list()

# Iterate over each column in the dataframe
for (col in colnames(numeric_data_no_outliers)) {
  # Prepare the data for plotting
  plot_data <- numeric_data_no_outliers %>%
    select(teamDistribution_encoded, .data[[col]])
  
  # Create the combined boxplot plot
  plot <- ggplot(plot_data, aes(x = factor(teamDistribution_encoded), y = .data[[col]], fill = factor(teamDistribution_encoded))) +
    geom_boxplot() +
    labs(title = col, x = "Category", y = NULL) +
    theme_minimal() +
    facet_wrap(~ teamDistribution_encoded, labeller = labeller(teamDistribution_encoded = c("0" = "Local", "1" = "Global")))
  
  # Add the plot to the list
  combined_boxplots[[col]] <- plot
}

# View the combined boxplot plots
combined_boxplots


```{r}
print(numeric_data_no_outliers)

```
/*
/*
library(ggplot2)
# Create an empty list to store the plots
plots <- list()

# Iterate over each column in the dataframe
for (col in colnames(numeric_data_no_outliers)) {
  # Create a boxplot for the current column
  plot <- ggplot(numeric_data_no_outliers, aes(x = 1, y = .data[[col]])) +
    geom_boxplot() +
    labs(title = col, x = NULL, y = NULL) +
    theme_light() +
   theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
  
  # Add the plot to the list
  plots[[col]] <- plot
}

# Display the boxplots
for (col in colnames(numeric_data_no_outliers)) {
  print(plots[[col]])
}
*/

```{r}
numeric_data_no_outliers$femaleTeamMembersPercent <- as.numeric(numeric_data_no_outliers$femaleTeamMembersPercent)
numeric_data_no_outliers$meetingHoursTotal <- as.numeric(numeric_data_no_outliers$meetingHoursTotal)
numeric_data_no_outliers$inPersonMeetingHoursTotal <- as.numeric(numeric_data_no_outliers$inPersonMeetingHoursTotal)
numeric_data_no_outliers$nonCodingDeliverablesHoursTotal <- as.numeric(numeric_data_no_outliers$nonCodingDeliverablesHoursTotal)
numeric_data_no_outliers$codingDeliverablesHoursTotal <- as.numeric(numeric_data_no_outliers$codingDeliverablesHoursTotal)
numeric_data_no_outliers$helpHoursTotal <- as.numeric(numeric_data_no_outliers$helpHoursTotal)
numeric_data_no_outliers$globalLeadAdminHoursTotal <- as.numeric(numeric_data_no_outliers$globalLeadAdminHoursTotal)
numeric_data_no_outliers$uniqueCommitMessagePercent <- as.numeric(numeric_data_no_outliers$uniqueCommitMessagePercent)
```



library(dplyr)

# Create a list to store the density plots
density_plots <- list()

# Iterate over each column in the dataframe
for (col in colnames(numeric_data_no_outliers)) {
  # Calculate mean and standard deviation for the current column
  mean_val <- mean(numeric_data_no_outliers[[col]])
  sd_val <- sd(numeric_data_no_outliers[[col]])

  # Create a density plot for the current column
  plot <- ggplot(numeric_data_no_outliers, aes(x = .data[[col]], fill = col)) +
    geom_density(alpha = 0.5) +
    stat_function(fun = dnorm, args = list(mean = mean_val, sd = sd_val),
                  color = "blue", linetype = "dashed", size = 1) +
    labs(title = col, x = col, y = "Density") +
    theme_minimal()

  # Add the plot to the list
  density_plots[[col]] <- plot
}

# View the density plots
density_plots


```{r}
str(numeric_data_no_outliers)
```

```{r}

library(moments)
library(ggplot2)

# Columns to check for normality
columns_to_check <- colnames(numeric_data_no_outliers)

# Iterate over the columns
for (col_name in columns_to_check) {
  column <- numeric_data_no_outliers[[col_name]]
  
  # Skip columns with only one unique value
  if (length(unique(column)) <= 1) {
    warning(paste("Column", col_name, "has only one unique value. Skipping."))
    next
  }
  
  # Perform Shapiro-Wilk test for normality
  shapiro_test <- shapiro.test(column)
  
  # Check p-value of the test
  p_value <- shapiro_test$p.value
  
  # If p-value is less than the significance level (0.05), the data is not normal
  if (p_value < 0.05) {
    # Initialize variables for storing transformation results
    transformed_column <- NULL
    best_skewness <- Inf
    
    # Apply different transformations and select the best one based on skewness
    transformations <- list(
      identity = column,
      logarithmic = log(column + 1),
      square_root = sqrt(column),
      rank = rank(column)
    )
    
    for (transformation_name in names(transformations)) {
      transformed_data <- transformations[[transformation_name]]
      
      # Check for NaN values in the transformed data
      if (!any(is.nan(transformed_data))) {
        skewness <- skewness(transformed_data)
        
        # Update the best transformation if skewness is lower
        if (abs(skewness) < abs(best_skewness)) {
          transformed_column <- transformed_data
          best_skewness <- skewness
        }
      }
    }
    
    # Replace the original column with the best transformed values
    if (!is.null(transformed_column)) {
      numeric_data_no_outliers[[col_name]] <- transformed_column
    }
  }
 
}

```



# Create a list to store the density plots
density_plots <- list()

# Iterate over each column in the dataframe
for (col in colnames(numeric_data_no_outliers)) {
  # Calculate mean and standard deviation for the current column
  mean_val <- mean(numeric_data_no_outliers[[col]])
  sd_val <- sd(numeric_data_no_outliers[[col]])

  # Create a density plot for both categories
  plot <- ggplot(numeric_data_no_outliers, aes(x = .data[[col]], fill = col)) +
    geom_density(alpha = 0.5) +
    stat_function(fun = dnorm, args = list(mean = mean_val, sd = sd_val),
                  color = "blue", linetype = "dashed", size = 1) +
    labs(title = col, x = col, y = "Density") +
    theme_minimal() +
    facet_wrap(~ teamDistribution_encoded, labeller = labeller(teamDistribution_encoded = c("0" = "Local", "1" = "Global")))

  # Add the plot to the list
  density_plots[[col]] <- plot
}

# View the density plots
density_plots



```{r}
Pearson_correlation<- cor(numeric_data_no_outliers, method = "pearson")
print(Pearson_correlation)

```

```{r}
str(Pearson_correlation)
```

```{r}
library(ggplot2)

# Calculate Pearson correlation matrix
Pearson_correlation <- cor(numeric_data_no_outliers, method = "pearson")

# Create a data frame for the correlation heatmap
heatmap_data <- reshape2::melt(Pearson_correlation)

# Rename the columns
colnames(heatmap_data) <- c("Var1", "Var2", "Correlation")

# Create the heatmap plot
heatmap <- ggplot(heatmap_data, aes(x = Var1, y = Var2, fill = Correlation)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.1f", Correlation)), color = "black", size = 3) +
  ggtitle("Correlation Heatmap") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_gradient2(low = "yellow", mid = "orange", high = "red", midpoint = 0) +
  labs(fill = "Correlation")

print(heatmap)

```
```{r}

library(ggplot2)
# Calculate Pearson correlation matrix
Pearson_correlation <- cor(numeric_data_no_outliers, method = "pearson")

# Create a data frame for the correlation heatmap
heatmap_data <- reshape2::melt(Pearson_correlation)

# Rename the columns
colnames(heatmap_data) <- c("Var1", "Var2", "Correlation")

# Filter the data based on the threshold
threshold <- 0.6
filtered_data <- heatmap_data[abs(heatmap_data$Correlation) > threshold, ]

# Create the filtered heatmap plot
filtered_heatmap <- ggplot(filtered_data, aes(x = Var1, y = Var2, fill = Correlation)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.1f", Correlation)), color = "black", size = 3) +
  ggtitle("Correlation Heatmap (Threshold > 0.6)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_gradient2(low = "yellow", mid = "orange", high = "red", midpoint = 0) +
  labs(fill = "Correlation")

print(filtered_heatmap)

```

```{r}
library(ggplot2)

# Calculate Pearson correlation matrix
Pearson_correlation <- cor(numeric_data_no_outliers, method = "pearson")

# Create a data frame for the correlation heatmap
heatmap_data <- reshape2::melt(Pearson_correlation)

# Rename the columns
colnames(heatmap_data) <- c("Var1", "Var2", "Correlation")

# Filter the data based on the threshold
threshold <- 0.5
filtered_data <- heatmap_data[abs(heatmap_data$Correlation) <= threshold, ]

# Create the filtered heatmap plot
filtered_heatmap <- ggplot(filtered_data, aes(x = Var1, y = Var2, fill = Correlation)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.1f", Correlation)), color = "black", size = 3) +
  ggtitle("Correlation Heatmap (Threshold <= 0.5)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_gradient2(low = "yellow", mid = "orange", high = "red", midpoint = 0) +
  labs(fill = "Correlation")

print(filtered_heatmap)

```

'teamMemberCount'
'femaleTeamMembersPercent'
'teamMemberResponseCount' => remove by correlation
'meetingHoursTotal'
'inPersonMeetingHoursTotal' => remove by correlation
'nonCodingDeliverablesHoursTotal' => remove by correlation
'codingDeliverablesHoursTotal'
'helpHoursTotal' => remove by correlation
'globalLeadAdminHoursTotal'
'leadAdminHoursResponseCount' => remove by correlation
'globalLeadAdminHoursResponseCount'
'commitCount'
'uniqueCommitMessageCount' => remove by correlation
'uniqueCommitMessagePercent' => remove by correlation
'commitMessageLengthTotal' => remove by correlation
'issueCount'
'onTimeIssueCount' => remove by correlation
'teamDistribution_encoded' => remove by correlation



```{r}
# Subset the desired columns from T1_data
categorical_data <- T1_data[, c('teamLeadGender', 'teamDistribution', 'productLetterGrade')]

for (col in colnames(categorical_data)) {
  plot_data <- table(categorical_data[[col]])
  plot_df <- data.frame(x = names(plot_data), y = as.vector(plot_data))
  
  plot <- ggplot(plot_df, aes(x, y)) +
    geom_bar(stat = "identity", fill = "steelblue",width = 0.5) +
    labs(x = col, y = "Count") +
    ggtitle(paste("Bar Plot of", col))
  
  print(plot)
}
```

```{r}
# Define the variables for the goodness-of-fit test
variables <- c("teamLeadGender", "teamDistribution", "productLetterGrade")

# Perform the goodness-of-fit test for each variable
for (var in variables) {
  # Create a contingency table of observed frequencies for the current variable
  observed <- table(categorical_data[[var]])
  
  # Define the expected probabilities for the current variable (binomial distribution)
  expected_prob <- c(0.5, 0.5)  # Assuming a 50/50 distribution
  
  # Calculate the expected frequencies based on the expected probabilities
  expected <- expected_prob * sum(observed)
  
  # Perform the chi-square goodness-of-fit test
  chi_square_test <- chisq.test(observed, p = expected_prob)
  
  # Print the test results
  cat("Variable:", var, "\n")
  print(chi_square_test)
  cat("\n")
}

```





'teamMemberCount'
'femaleTeamMembersPercent'
'teamMemberResponseCount' => remove by correlation
'meetingHoursTotal'
'inPersonMeetingHoursTotal' => remove by correlation
'nonCodingDeliverablesHoursTotal' => remove by correlation
'codingDeliverablesHoursTotal'
'helpHoursTotal' => remove by correlation
'globalLeadAdminHoursTotal'
'leadAdminHoursResponseCount' => remove by correlation
'globalLeadAdminHoursResponseCount' => remove by correlation
'commitCount'
'uniqueCommitMessageCount' => remove by correlation
'uniqueCommitMessagePercent' => remove by correlation
'commitMessageLengthTotal' => remove by correlation
'issueCount'
'onTimeIssueCount' => remove by correlation
'teamDistribution_encoded' => remove by correlation


```{r}
predictor_vars <- c('teamMemberCount', 'femaleTeamMembersPercent', 'meetingHoursTotal','inPersonMeetingHoursTotal','nonCodingDeliverablesHoursTotal','helpHoursTotal','teamMemberResponseCount', 'codingDeliverablesHoursTotal','leadAdminHoursResponseCount',
'globalLeadAdminHoursResponseCount' ,'globalLeadAdminHoursTotal', 'commitCount', 'issueCount', 'teamDistribution_encoded','uniqueCommitMessageCount','uniqueCommitMessagePercent','onTimeIssueCount',
'commitMessageLengthTotal','teamDistribution_encoded')

# Perform ANOVA for each predictor variable
for (var in predictor_vars) {
  anova_result <- anova(lm(productLetterGrade_encoded ~ ., data = numeric_data_no_outliers[, c(var, "productLetterGrade_encoded")]))
  cat("ANOVA results for", var, ":\n")
  print(anova_result)
  cat("\n")
}
```

```{r}
print(numeric_data_no_outliers)
```

```{r}

# Extract the specified columns from numeric_data_no_outliers
X <- numeric_data_no_outliers[, c('teamMemberCount', 'femaleTeamMembersPercent', 'meetingHoursTotal','inPersonMeetingHoursTotal','nonCodingDeliverablesHoursTotal','helpHoursTotal','teamMemberResponseCount', 'codingDeliverablesHoursTotal','leadAdminHoursResponseCount',
'globalLeadAdminHoursResponseCount' ,'globalLeadAdminHoursTotal', 'commitCount', 'issueCount', 'teamDistribution_encoded','uniqueCommitMessageCount','uniqueCommitMessagePercent','onTimeIssueCount',
'commitMessageLengthTotal')]

# y contains the response variable
y <- numeric_data_no_outliers$productLetterGrade_encoded

# Fit the multiple linear regression model
model <- lm(y ~ ., data = X)

# Print the regression results
summary(model)



```

```{r}
T1_data$teamLeadGender_encoded <- ifelse(T1_data$teamLeadGender == "F", 0, 1)

# Subset T1_data to match the number of rows in numeric_data_no_outliers
T1_data_subset <- T1_data[1:nrow(numeric_data_no_outliers), ]

# Add the encoded column to numeric_data_no_outliers
numeric_data_no_outliers$productLetterGrade_encoded <- T1_data_subset$productLetterGrade_encoded

# Print numeric_data_no_outliers
print(numeric_data_no_outliers)


```



```{r}
selected_columns <- c("femaleTeamMembersPercent", "meetingHoursTotal", "codingDeliverablesHoursTotal", "globalLeadAdminHoursTotal", "commitCount", "issueCount", "teamLeadGender_encoded","teamDistribution_encoded", "productLetterGrade_encoded")
selected_data <-numeric_data_no_outliers[, selected_columns]

output_file <- "T1_features_final.csv"
write.csv(selected_data, file = output_file, row.names = FALSE)
```







current_dir <- getwd()
print(current_dir)



